---
title: "Example 2"
author: "Eduardo F. Mioto de O dos Santos"
date: "4 de julho de 2017"
output:
  html_document: default
---

# install.packages("ggplot2", dependencies = TRUE)
#	install.packages('Rmisc', dependencies = TRUE)
# install.packages("gridExtra")

```{r setup, include=FALSE}

# Read CSV into R
ece <- read.csv(file="C:/Users/<<user>>/Documents/GitHub/r-sandbox/example-2/example2.csv", header=TRUE, sep=",")

source('C:/Users/<<user>>/Documents/GitHub/r-sandbox/multiplot.R')
```

```{r include, echo=FALSE, results='hide',message=FALSE}
library(ggplot2)
library(Rcmdr)
library(datasets)
library(nortest)
library(knitr)

```

## Outliers

COUPLING_BETWEEN_OBJECTS
```{r echo = FALSE}
  variable <- ece$COUPLING_BETWEEN_OBJECTS
  deviation	<- sd(variable)
  limSup = (deviation*3) + mean(variable) 
  limInf = mean(variable) - (deviation*3);  
  outliers <- which(variable > limSup | variable < limInf)
  eceClean <- subset(ece, ece$COUPLING_BETWEEN_OBJECTS < limSup)
  eceClean <- subset(ece, ece$COUPLING_BETWEEN_OBJECTS > limInf)
  
  medium <- matrix(c(deviation*3, mean(variable), limInf, limSup, length(outliers)),	ncol=5)
  colnames(medium) <- c('3sigma', 'Média', 'Lim Inferior', 'Lim Superior', 'Nro Outliers')
  rownames(medium) <- c('')
  medium.table 	<- as.table(medium)
  medium
```

DEPTH_INHERITANCE
```{r echo = FALSE }
  variable <- ece$DEPTH_INHERITANCE
  deviation	<- sd(variable)
  limSup = (deviation*3) + mean(variable) 
  limInf = mean(variable) - (deviation*3);  
  outliers <- which(variable > limSup | variable < limInf)
  eceClean <- subset(eceClean, DEPTH_INHERITANCE < limSup)
  eceClean <- subset(eceClean, DEPTH_INHERITANCE > limInf)
  
  medium <- matrix(c(deviation*3, mean(variable), limInf, limSup, length(outliers)),	ncol=5)
  colnames(medium) <- c('3sigma', 'Média', 'Lim Inferior', 'Lim Superior', 'Nro Outliers')
  rownames(medium) <- c('')
  medium.table 	<- as.table(medium)
  medium
```

LACK_OF_COHESION_OF_METHODS
```{r echo = FALSE }
  variable <- ece$LACK_OF_COHESION_OF_METHODS
  deviation	<- sd(variable)
  limSup = (deviation*3) + mean(variable) 
  limInf = mean(variable) - (deviation*3);  
  outliers <- which(variable > limSup | variable < limInf)
  eceClean <- subset(eceClean, LACK_OF_COHESION_OF_METHODS < limSup)
  eceClean <- subset(eceClean, LACK_OF_COHESION_OF_METHODS > limInf)
  
  medium <- matrix(c(deviation*3, mean(variable), limInf, limSup, length(outliers)),	ncol=5)
  colnames(medium) <- c('3sigma', 'Média', 'Lim Inferior', 'Lim Superior', 'Nro Outliers')
  rownames(medium) <- c('')
  medium.table 	<- as.table(medium)
  medium
```


FAN_IN
```{r echo = FALSE }
  variable <- ece$FAN_IN
  deviation	<- sd(variable)
  limSup = (deviation*3) + mean(variable) 
  limInf = mean(variable) - (deviation*3);  
  outliers <- which(variable > limSup | variable < limInf)
  eceClean <- subset(eceClean, FAN_IN < limSup)
  eceClean <- subset(eceClean, FAN_IN > limInf)
  
  medium <- matrix(c(deviation*3, mean(variable), limInf, limSup, length(outliers)),	ncol=5)
  colnames(medium) <- c('3sigma', 'Média', 'Lim Inferior', 'Lim Superior', 'Nro Outliers')
  rownames(medium) <- c('')
  medium.table 	<- as.table(medium)
  medium
```

RESPONSE_FOR_CLASS
```{r echo = FALSE }
  variable <- ece$RESPONSE_FOR_CLASS
  deviation	<- sd(variable)
  limSup = (deviation*3) + mean(variable) 
  limInf = mean(variable) - (deviation*3);  
  outliers <- which(variable > limSup | variable < limInf)
  eceClean <- subset(eceClean, RESPONSE_FOR_CLASS < limSup)
  eceClean <- subset(eceClean, RESPONSE_FOR_CLASS > limInf)
  
  medium <- matrix(c(deviation*3, mean(variable), limInf, limSup, length(outliers)),	ncol=5)
  colnames(medium) <- c('3sigma', 'Média', 'Lim Inferior', 'Lim Superior', 'Nro Outliers')
  rownames(medium) <- c('')
  medium.table 	<- as.table(medium)
  medium
```

WEIGHTED_METHODS_PER_CLASS
```{r echo = FALSE }
  variable <- ece$WEIGHTED_METHODS_PER_CLASS
  deviation	<- sd(variable)
  limSup = (deviation*3) + mean(variable) 
  limInf = mean(variable) - (deviation*3);  
  outliers <- which(variable > limSup | variable < limInf)
  eceClean <- subset(eceClean, WEIGHTED_METHODS_PER_CLASS < limSup)
  eceClean <- subset(eceClean, WEIGHTED_METHODS_PER_CLASS > limInf)
  
  medium <- matrix(c(deviation*3, mean(variable), limInf, limSup, length(outliers)),	ncol=5)
  colnames(medium) <- c('3sigma', 'Média', 'Lim Inferior', 'Lim Superior', 'Nro Outliers')
  rownames(medium) <- c('')
  medium.table 	<- as.table(medium)
  medium
```

sumLOC_TOTAL
```{r echo = FALSE }
  variable <- ece$sumLOC_TOTAL
  deviation	<- sd(variable)
  limSup = (deviation*3) + mean(variable) 
  limInf = mean(variable) - (deviation*3);  
  outliers <- which(variable > limSup | variable < limInf)
  eceClean <- subset(eceClean, sumLOC_TOTAL < limSup)
  eceClean <- subset(eceClean, sumLOC_TOTAL > limInf)
  
  medium <- matrix(c(deviation*3, mean(variable), limInf, limSup, length(outliers)),	ncol=5)
  colnames(medium) <- c('3sigma', 'Média', 'Lim Inferior', 'Lim Superior', 'Nro Outliers')
  rownames(medium) <- c('')
  medium.table 	<- as.table(medium)
  medium
```


NUMDEFECTS
```{r echo = FALSE }
  variable <- ece$NUMDEFECTS
  deviation	<- sd(variable)
  limSup = (deviation*3) + mean(variable) 
  limInf = mean(variable) - (deviation*3);  
  outliers <- which(variable > limSup | variable < limInf)
  eceClean <- subset(eceClean, NUMDEFECTS < limSup)
  eceClean <- subset(eceClean, NUMDEFECTS > limInf)
  
  medium <- matrix(c(deviation*3, mean(variable), limInf, limSup, length(outliers)),	ncol=5)
  colnames(medium) <- c('3 Sigma;', 'Média', 'Lim Inferior', 'Lim Superior', 'Nro Outliers')
  rownames(medium) <- c('')
  medium.table 	<- as.table(medium)
  medium
```

### A 1.1) Correlações - Spearman

```{r}
cor(eceClean[unlist(lapply(eceClean, is.numeric))], method = "spearman")
```

### A 1.2) Correlações - Pearson

```{r}
cor(eceClean[unlist(lapply(eceClean, is.numeric))], method = "pearson")
```

### B)  

```{r}
chisq.test(eceClean$DEPTH_INHERITANCE, eceClean$NUMDEFECTS, correct=FALSE)  
```
### C)  

```{r}

kruskal.test(list(eceClean$NUMDEFECTS, eceClean$LACK_OF_COHESION_OF_METHODS, eceClean$DEPTH_INHERITANCE))
kruskal.test(eceClean$NUMDEFECTS ~ eceClean$LACK_OF_COHESION_OF_METHODS, data = eceClean) 
kruskal.test(eceClean$NUMDEFECTS ~ eceClean$DEPTH_INHERITANCE, data = eceClean) 
kruskal.test(eceClean$LACK_OF_COHESION_OF_METHODS ~ eceClean$DEPTH_INHERITANCE, data = eceClean) 

```
### D)  


```{r echo = FALSE}
# Fit our regression model
mod <- lm(eceClean$NUMDEFECTS ~ eceClean$sumLOC_TOTAL + eceClean$WEIGHTED_METHODS_PER_CLASS, 
          data=eceClean)
summary(mod) # show regression coefficients table

```

## Anexos D) Regressão Linear

* Correlações (Spearman): 
* DEPTH_INHERITANCE                 <0.9342193> FAN_IN
* COUPLING_BETWEEN_OBJECTS          <0.8151521> sumLOC_TOTAL
* DEPTH_INHERITANCE                 <0.7348442> RESPONSE_FOR_CLASS
* FAN_IN                            <0.7208096> RESPONSE_FOR_CLASS
* WEIGHTED_METHODS_PER_CLASS        <0.6258510> RESPONSE_FOR_CLASS

```{r echo = FALSE}
# Fit our regression model
mod <- lm(eceClean$DEPTH_INHERITANCE ~ eceClean$FAN_IN, # regression formula
              data=eceClean) # data set
# Summarize and print the results
summary(mod) # show regression coefficients table
```

- DEPTH_INHERITANCE <0.9342193> FAN_IN
```{r echo = FALSE}
p1 <- ggplot(ece, aes(x=ece$DEPTH_INHERITANCE, y=ece$FAN_IN)) +
geom_point() +
ggtitle("Original") +
xlab("DEPTH_INHERITANCE") +
ylab("FAN_IN") +
geom_smooth(method='lm')

p2 <- ggplot(eceClean, aes(x=eceClean$DEPTH_INHERITANCE, y=eceClean$FAN_IN)) +
geom_point() +
ggtitle("Sem Outliers") +
xlab("DEPTH_INHERITANCE") +
ylab("FAN_IN") +
geom_smooth(method='lm')

multiplot(p1, p2, cols=2)
```


- COUPLING_BETWEEN_OBJECTS <0.8151521> sumLOC_TOTAL
```{r echo = FALSE}
p1 <- ggplot(ece, aes(x=ece$COUPLING_BETWEEN_OBJECTS, y=ece$sumLOC_TOTAL)) +
geom_point() +
ggtitle("Original") +
xlab("COUPLING_BETWEEN_OBJECTS") +
ylab("sumLOC_TOTAL") +
geom_smooth(method=lm)
 
p2 <- ggplot(eceClean, aes(x=eceClean$COUPLING_BETWEEN_OBJECTS, y=eceClean$sumLOC_TOTAL)) +
geom_point() +
ggtitle("Sem Outliers") +
xlab("COUPLING_BETWEEN_OBJECTS") +
ylab("sumLOC_TOTAL") +
geom_smooth(method=lm)

multiplot(p1, p2, cols=2)
```


- DEPTH_INHERITANCE <0.7348442> RESPONSE_FOR_CLASS
```{r echo = FALSE}
p1 <- ggplot(ece, aes(x=ece$DEPTH_INHERITANCE, y=ece$RESPONSE_FOR_CLASS)) +
geom_point() +
ggtitle("Original") +
xlab("COUPLING_BETWEEN_OBJECTS") +
ylab("sumLOC_TOTAL") +
geom_smooth(method=lm)
 
p2 <- ggplot(eceClean, aes(x=eceClean$DEPTH_INHERITANCE, y=eceClean$RESPONSE_FOR_CLASS)) +
geom_point() +
ggtitle("Sem Outliers") +
xlab("COUPLING_BETWEEN_OBJECTS") +
ylab("sumLOC_TOTAL") +
geom_smooth(method=lm)

multiplot(p1, p2, cols=2)
```


- FAN_IN <0.7208096> RESPONSE_FOR_CLASS
```{r echo = FALSE}
p1 <- ggplot(ece, aes(x=ece$FAN_IN, y=ece$RESPONSE_FOR_CLASS)) +
geom_point() +
ggtitle("Original") +
xlab("FAN_IN") +
ylab("sumLOC_TOTAL") +
geom_smooth(method=lm)
 
p2 <- ggplot(eceClean, aes(x=eceClean$FAN_IN, y=eceClean$RESPONSE_FOR_CLASS)) +
geom_point() +
ggtitle("Sem Outliers") +
xlab("FAN_IN") +
ylab("sumLOC_TOTAL") +
geom_smooth(method=lm)

multiplot(p1, p2, cols=2)
```


- WEIGHTED_METHODS_PER_CLASS <0.6258510> RESPONSE_FOR_CLASS
```{r echo = FALSE}
p1 <- ggplot(ece, aes(x=ece$WEIGHTED_METHODS_PER_CLASS, y=ece$RESPONSE_FOR_CLASS)) +
geom_point() +
ggtitle("Original") +
xlab("WEIGHTED_METHODS_PER_CLASS") +
ylab("RESPONSE_FOR_CLASS") +
geom_smooth(method=lm)
 
p2 <- ggplot(eceClean, aes(x=eceClean$WEIGHTED_METHODS_PER_CLASS, y=eceClean$RESPONSE_FOR_CLASS)) +
geom_point() +
ggtitle("Sem Outliers") +
xlab("WEIGHTED_METHODS_PER_CLASS") +
ylab("RESPONSE_FOR_CLASS") +
geom_smooth(method=lm)

multiplot(p1, p2, cols=2)
```


### Anexo Análise Visual

```{r echo = FALSE}
### Histograma COUPLING_BETWEEN_OBJECTS
p1 <- ggplot(data=ece, aes(x =  ece$COUPLING_BETWEEN_OBJECTS)) +
geom_histogram(binwidth=1, position="dodge") +
ggtitle("Original") +
xlab("COUPLING BETWEEN OBJECTS") +
ylab("Quantidade")

p2 <- ggplot(data=eceClean, aes(x =  eceClean$COUPLING_BETWEEN_OBJECTS)) +
geom_histogram(binwidth=1, position="dodge") +
ggtitle("Sem Outliers") +
xlab("COUPLING BETWEEN OBJECTS") +
ylab("Quantidade")

multiplot(p1, p2, cols=2)
```


```{r echo = FALSE}
### Histograma LACK_OF_COHESION_OF_METHODS
p1 <- ggplot(data=ece, aes(x =  ece$LACK_OF_COHESION_OF_METHODS)) +
geom_histogram(binwidth=2, position="dodge") +
ggtitle("Original") +
xlab("LACK_OF_COHESION_OF_METHODS") +
ylab("Quantidade")

p2 <- ggplot(data=eceClean, aes(x =  eceClean$LACK_OF_COHESION_OF_METHODS)) +
geom_histogram(binwidth=2, position="dodge") +
ggtitle("Sem Outliers") +
xlab("LACK_OF_COHESION_OF_METHODS") +
ylab("Quantidade")

multiplot(p1, p2, cols=2)
```


```{r echo = FALSE}
### Histograma FAN_IN
p1 <- ggplot(data=ece, aes(x =  ece$FAN_IN)) +
geom_histogram(binwidth=0.1, position="dodge") +
ggtitle("Original") +
xlab("FAN_IN") +
ylab("Quantidade")

p2 <- ggplot(data=eceClean, aes(x =  eceClean$FAN_IN)) +
geom_histogram(binwidth=0.1, position="dodge") +
ggtitle("Sem Outliers") +
xlab("FAN_IN") +
ylab("Quantidade")

multiplot(p1, p2, cols=2)
```


```{r echo = FALSE}
### Histograma RESPONSE_FOR_CLASS
p1 <- ggplot(data=ece, aes(x =  ece$RESPONSE_FOR_CLASS)) +
geom_histogram(binwidth=5, position="dodge") +
ggtitle("Original") +
xlab("RESPONSE_FOR_CLASS") +
ylab("Quantidade")

p2 <- ggplot(data=eceClean, aes(x =  eceClean$RESPONSE_FOR_CLASS)) +
geom_histogram(binwidth=4, position="dodge") +
ggtitle("Sem Outliers") +
xlab("RESPONSE_FOR_CLASS") +
ylab("Quantidade")

multiplot(p1, p2, cols=2)
```


```{r echo = FALSE}
### Histograma WEIGHTED_METHODS_PER_CLASS
p1 <- ggplot(data=ece, aes(x =  ece$WEIGHTED_METHODS_PER_CLASS)) +
geom_histogram(binwidth=2, position="dodge") +
ggtitle("Original") +
xlab("WEIGHTED_METHODS_PER_CLASS") +
ylab("Quantidade")

p2 <- ggplot(data=eceClean, aes(x =  eceClean$WEIGHTED_METHODS_PER_CLASS)) +
geom_histogram(binwidth=2, position="dodge") +
ggtitle("Sem Outliers") +
xlab("WEIGHTED_METHODS_PER_CLASS") +
ylab("Quantidade")

multiplot(p1, p2, cols=2)
```


```{r echo = FALSE}
### Histograma Discrepância
p1 <- ggplot(data=ece, aes(x =  ece$sumLOC_TOTAL)) +
geom_histogram(binwidth=100, position="dodge") +
ggtitle("Original") +
xlab("SUM LOC Total") +
ylab("Quantidade")

p2 <- ggplot(data=eceClean, aes(x =  eceClean$sumLOC_TOTAL)) +
geom_histogram(binwidth=100, position="dodge") +
ggtitle("Sem Outliers") +
xlab("SUM LOC Total") +
ylab("Quantidade")

multiplot(p1, p2, cols=2)
```


```{r echo = FALSE}
### Histograma NUMDEFECTS
p1 <- ggplot(data=ece, aes(x =  ece$NUMDEFECTS)) +
geom_histogram(binwidth=2, position="dodge") +
ggtitle("Original") +
xlab("NUMDEFECTS") +
ylab("Quantidade")

p2 <- ggplot(data=eceClean, aes(x =  eceClean$NUMDEFECTS)) +
geom_histogram(binwidth=2, position="dodge") +
ggtitle("Sem Outliers") +
xlab("NUMDEFECTS") +
ylab("Quantidade")

multiplot(p1, p2, cols=2)
```


```{r echo = FALSE}
p1 <- ggplot(ece, aes(x=ece$COUPLING_BETWEEN_OBJECTS, y=ece$NUMDEFECTS)) +
geom_point() +
ggtitle("Original") +
xlab("COUPLING_BETWEEN_OBJECTS") +
ylab("NUMDEFECTS") +
geom_smooth(method=lm) 

p2 <- ggplot(eceClean, aes(x=eceClean$COUPLING_BETWEEN_OBJECTS, y=eceClean$NUMDEFECTS)) +
geom_point() +
ggtitle("Sem Outliers") +
xlab("COUPLING_BETWEEN_OBJECTS") +
ylab("NUMDEFECTS") +
geom_smooth(method=lm) 

multiplot(p1, p2, cols=2)
```


```{r echo = FALSE}
p1 <- ggplot(ece, aes(x=ece$DEPTH_INHERITANCE, y=ece$NUMDEFECTS)) +
geom_point() +
ggtitle("Original") +
xlab("DEPTH_INHERITANCE") +
ylab("NUMDEFECTS") +
geom_smooth(method=lm) 

p2 <- ggplot(eceClean, aes(x=eceClean$DEPTH_INHERITANCE, y=eceClean$NUMDEFECTS)) +
geom_point() +
ggtitle("Sem Outliers") +
xlab("DEPTH_INHERITANCE") +
ylab("NUMDEFECTS") +
geom_smooth(method=lm) 

multiplot(p1, p2, cols=2)
```


```{r echo = FALSE}
p1 <- ggplot(ece, aes(x=ece$LACK_OF_COHESION_OF_METHODS, y=ece$NUMDEFECTS)) +
geom_point() +
ggtitle("Original") +
xlab("LACK_OF_COHESION_OF_METHODS") +
ylab("NUMDEFECTS") +
geom_smooth(method=lm) 

p2 <- ggplot(eceClean, aes(x=eceClean$LACK_OF_COHESION_OF_METHODS, y=eceClean$NUMDEFECTS)) +
geom_point() +
ggtitle("Sem Outliers") +
xlab("LACK_OF_COHESION_OF_METHODS") +
ylab("NUMDEFECTS") +
geom_smooth(method=lm) 

multiplot(p1, p2, cols=2)
```


```{r echo = FALSE}
p1 <- ggplot(ece, aes(x=ece$FAN_IN, y=ece$NUMDEFECTS)) +
geom_point() +
ggtitle("Original") +
xlab("FAN_IN") +
ylab("NUMDEFECTS") +
geom_smooth(method=lm) 

p2 <- ggplot(eceClean, aes(x=eceClean$FAN_IN, y=eceClean$NUMDEFECTS)) +
geom_point() +
ggtitle("Sem Outliers") +
xlab("FAN_IN") +
ylab("NUMDEFECTS") +
geom_smooth(method=lm) 

multiplot(p1, p2, cols=2)
```


```{r echo = FALSE}
p1 <- ggplot(ece, aes(x=ece$RESPONSE_FOR_CLASS, y=ece$NUMDEFECTS)) +
geom_point() +
ggtitle("Original") +
xlab("RESPONSE_FOR_CLASS") +
ylab("NUMDEFECTS") +
geom_smooth(method=lm) 

p2 <- ggplot(eceClean, aes(x=eceClean$RESPONSE_FOR_CLASS, y=eceClean$NUMDEFECTS)) +
geom_point() +
ggtitle("Sem Outliers") +
xlab("RESPONSE_FOR_CLASS") +
ylab("NUMDEFECTS") +
geom_smooth(method=lm) 

multiplot(p1, p2, cols=2)
```


```{r echo = FALSE}
p1 <- ggplot(ece, aes(x=ece$WEIGHTED_METHODS_PER_CLASS, y=ece$NUMDEFECTS)) +
geom_point() +
ggtitle("Original") +
xlab("WEIGHTED_METHODS_PER_CLASS") +
ylab("NUMDEFECTS") +
geom_smooth(method=lm) 

p2 <- ggplot(eceClean, aes(x=eceClean$WEIGHTED_METHODS_PER_CLASS, y=eceClean$NUMDEFECTS)) +
geom_point() +
ggtitle("Sem Outliers") +
xlab("WEIGHTED_METHODS_PER_CLASS") +
ylab("NUMDEFECTS") +
geom_smooth(method=lm) 

multiplot(p1, p2, cols=2)
```


```{r echo = FALSE}
p1 <- ggplot(ece, aes(x=ece$sumLOC_TOTAL, y=ece$NUMDEFECTS)) +
geom_point() +
ggtitle("Original") +
xlab("sumLOC_TOTAL") +
ylab("NUMDEFECTS") +
geom_smooth(method=lm)
 
p2 <- ggplot(eceClean, aes(x=eceClean$sumLOC_TOTAL, y=eceClean$NUMDEFECTS)) +
geom_point() +
ggtitle("Sem Outliers") +
xlab("sumLOC_TOTAL") +
ylab("NUMDEFECTS") +
geom_smooth(method=lm)

multiplot(p1, p2, cols=2)
```

### References
- http://staff.unak.is/andy/staticanalysis0809/metrics/overview.html
- https://www.r-bloggers.com/linear-regression-using-r/
- http://www.cookbook-r.com/Graphs/Multiple_graphs_on_one_page_(ggplot2)
